### 2022-05-03 paper/localpsf.tex
minor edits

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following four approximations, ordered by increasing level of sophistication:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) \label{eq:translate3}\\
\phi_x(y)/V(x) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) / V(x'). \label{eq:translate4}
\end{align}
Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization/CUR approximation \cite{CUR,NYSTROM}. However, the required rank in the low rank approximation can be large, which makes algorithms based on \eqref{eq:translate1} expensive.

>>>>

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following approximations:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) \label{eq:translate3}\\
\phi_x(y)/V(x) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) / V(x'). \label{eq:translate4}
\end{align}
These are four different ways to approximate an impulse response by a nearby impulse response, with each successive approximation building upon the previous ones. Our method uses \eqref{eq:translate4}, which is the most sophisticated of these approximations.

Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization/CUR approximation \cite{CUR,NYSTROM}. However, the required rank in the low rank approximation can be large, which makes algorithms based on \eqref{eq:translate1} expensive.
